Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-07-17 paper/SupMat.Rnw
continued work on responses and related edits to ms

>>>>

\section{Technical comments on notation}\label{SIsect:techcomm}

The quantities $E_i$, $C_{i \bs i}$, $E_i^\shp$, $C_{i \bs i}^\shp$, $E_i^\nat$, $C_{i \bs i}^\nat$
and related quantities are random variables, and hence notational conventions for random variables 
which are standard in fields of applied probability are used throughout the paper.
Relationships are considered intrinsic to random variable notation; for instance, though  
$E_i$, $E_i^\shp$, and $E_i^\nat$ have the same distribution, they are not the same as random variables
because of their different relationships with other random variables specified in the paper, e.g.,
$C_{i \bs i}$,  $C_{i \bs i}^\shp$, and $C_{i \bs i}^\nat$. Therefore the distributions
of the bivariate random variables $(E_i,C_{i \bs i})$, $(E_i^\shp,C_{i \bs i}^\shp)$, and
$(E_i^\nat,C_{i \bs i}^\nat)$ are all distinct, as are the random variables
$r(E_i,C_{i \bs i})$, $r(E_i^\shp,C_{i \bs i}^\shp)$, and $r(E_i^\nat,C_{i \bs i}^\nat)$.

\section{Uniqueness of our definition of ATA effects}\label{SIsect:uniqueness}

The description in the main text of how the distribution $(E_j^\nat, C_{j \bs i}^\nat)$
is constructed already reveals that a choice 
is made as to what type of correlation (e.g., Pearson, Spearman, etc.) is to be preserved
in the new distribution. Another choice is also made, though it is quite a canonical choice.
The choice involves the use of a bivariate normal distribution $(e_i,c_{i \bs i})$ 
with standard normal marginals (see Theory). Any other symmetrically tail associated bivariate 
distribution with standard normal marginals could also be used, instead, as $(e_i,c_{i \bs i})$ 
in our construction. For instance, one could form  $(e_i,c_{i \bs i})$ by using a
Frank copula \citep{Nelsen2006} to unite two standard normal univariate distributions. 
The bivariate normal distribution is a very natural choice, however, and other choices may 
be somewhat esoteric. We note that choices were present in MCT prior to our work. For instance, 
choices are often made in the definitions of $E$ and $C$ used \citep{Ellner_2019}. 
Our overall research point, that ATAs
\emph{can} be important for coexistence, is successfully made regardless of such choices, as long as 
reasonable choices were made, which they were.
